Dark matter halo shapes at $z=0$ in the Auriga simulations

### 2019-07-21 Document/paper.tex
references

The first effect that we put in evidence in this paper is the effect
of baryons in producing rounder DM halos.
This effect has been already widely reported in the literature.
It has been found that the strength of the change depends on the
numerical resolution, the method to resolve the hydrodynamics and the
models describing star formation and stellar feedback
\citep{Bailin05,Debattista08, Bryan13, Butsky16, Chua19, Artale19}.  
The key concept unifying these results is that the baryon distribution
influences and correlates with the dark matter halo shape. 
Indeed, as we presented in the previous section on the correlations
with disc properties, we find that the broad tendency is that extended
massive stellar discs correlate with spherical dark matter
distributions.

In contrast, it is more difficult to put into a broader context our
results on the halo-disc alignment.
\cite{JingSuto02} reported a shell alignment twisting in their dark
matter only simulations as measured in the direction changes of large
and medium shape axis. 
They only had three high resolution MW-like halos (with
$\sim 10^{6}$ inside the virial radius) and could not make a
statistical statement about the impact of this effect.
However, they see the twisting as an artifact resulting from high values of the
$b/a$ ratios that make the determination of the medium axis noisy.
For that reason we measured the twisting using the minor axis
alignments, however they do not report these alignments

\cite{Bailin05} used seven hydrodinamical simulations studied the disc
halo alignmnent as a function of radius.

\cite{Gomez17} studied this in Auriga.
\cite{Debattista13} reported a similar twisting effect, but only at radii smaller
than the disc radius. 
At radii larger than the disc radius, they find, the dark matter
shells stop twisting.

>>>>

The first effect that we put in evidence in this paper is the effect
of baryons in producing rounder DM halos.
This effect has been already widely reported in the literature.
It has been found that the strength of the change depends on the
numerical resolution, the gas cooling implementation and the
models describing star formation and stellar feedback
\citep{Kazantzidis04,Bailin05,Debattista08, Bryan13, Butsky16, Chua19, Artale19}.  
The key concept unifying these results is that the baryon distribution
influences and correlates with the dark matter halo shape. 
Indeed, as we presented in the previous section on the correlations
with disc properties, we find that the broad tendency is that extended
massive stellar discs correlate with spherical dark matter
distributions.

In contrast, there are fewer studies reporting on the halo-disc
alignment as a function of radius.
\cite{JingSuto02} reported a shell alignment twisting in their dark
matter only simulations as measured in the direction changes of large
and medium shape axis. 
They only had three high resolution MW-like halos (with
$\sim 10^{6}$ inside the virial radius) and could not make a
statistical statement about the impact of this effect.
However, they see the twisting as an artifact resulting from high values of the
$b/a$ ratios that make the determination of the medium axis noisy.
For that reason we measured the twisting using the minor axis
alignments, however they do not report these alignments.

\cite{Bailin05} used seven hydrodinamical simulations studied the disc
halo alignmnent as a function of radius.
For radii smaller than $0.1R_{200}$ they find a strong alignment
between the two minor axis of the halo and the disc. 
For larger radii the angle between the components changes showing a
weak correlation between the two components. 
\cite{Debattista13} performed a study on the disc-halo aligment
performing controled experiments on three different halos to study
changes the evolutionary change that drive the minor axis in the disc
and the halo to be aligned, their study by construction focuses only
on radii around $0.1R_{200}$.
Nevertheless, similarly to \cite{Bailin05}, they also report a strong
alignment in the region where the disc dominated.

\cite{Gomez17} studied this in Auriga.
